Mash screen results

### 2019-05-05 notebooks/Clustering analysis.Rmd
minor changes to headers and removed pacman library handling

```{r libraries, include = FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggtree)
library(cluster)
library(Biostrings)
library(ape)
library(tibble)
library(cowplot)
library(knitr)
library(vegan)
library(distanceR)
```

>>>>

```{r libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggtree)
library(cluster)
library(Biostrings)
library(ape)
library(tibble)
library(cowplot)
library(knitr)
library(vegan)
library(distanceR)
```

### 2019-05-05 notebooks/mash_analysis.Rmd
minor changes to headers and removed pacman library handling

---
title: "Quality control - Mash screen"
author: "Håkon Kaspersen"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
always_allow_html: yes
output:
    html_document:
      code_folding: hide
      df_print: paged
      highlight: kate
      number_sections: yes
      theme: flatly
      toc: yes
      toc_depth: 3
      toc_float:
        collapsed: yes
    pdf_document:
      toc: yes
      toc_depth: '3'
---

```{r}
pacman::p_load(ggplot2, dplyr, tidyr, stringr, purrr, viridis)
```

>>>>

---
title: "Mash screen results"
author: "Håkon Kaspersen"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
always_allow_html: yes
output:
    html_document:
      code_folding: hide
      df_print: paged
      highlight: kate
      number_sections: yes
      theme: flatly
      toc: yes
      toc_depth: 3
      toc_float:
        collapsed: yes
    pdf_document:
      toc: yes
      toc_depth: '3'
---

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(viridis)
```
